Hierarchical Lattice Structures with Tetrahedral Symmetry

### 2023-05-25 manuscript/main.tex
fast evaluation using ifft

\author{Adrian Lew}
\email{lewa@stanford.edu}
\affiliation{
  \institution{Stanford University}
  \streetaddress{440 Escondido Mall}
  \city{Stanford}
  \state{California}
  \country{USA}
  \postcode{94305}
}

@@

@@

\section{Discussion}
\subsection{Limitations}
\subsection{Future Work}

@@

>>>>

\author{Adrian J. Lew}
\email{lewa@stanford.edu}
\affiliation{
  \institution{Stanford University}
  \streetaddress{440 Escondido Mall}
  \city{Stanford}
  \state{California}
  \country{USA}
  \postcode{94305}
}

@@

\subsubsection{Weighted Averaging}

\subsubsection{Minkowski Sum and Difference}

@@

\section{Discussion}
\subsection{Limitations}
TODO continuity of implicit surface equations, enforcing continuity, etc.

TODO continuity of hybridization and transitions, how to pick transition path to enforce continuity, etc.

\subsection{Future Work}
TODO optimizing weight coefficients to achieve some target, i.e. porosity, stiffness, etc.

@@

A publically available implementation of this work is available at \url{https://github.com/rchensix/tetrahedral_implicit_lattice} under an MIT License. However, please note that while the implementation itself falls under an MIT License, methods and ideas mentioned in this paper are, at the time of writing, under consideration for a patent \cite{chen2022}.
